Police Shootings and Racism in America

### 2020-11-08 police_eda.Rmd
data cleaned again

# Recode officer races
all$OfficerRace <- gsub("H/L", "L", all$OfficerRace)
all$OfficerRace <- gsub("H", "L", all$OfficerRace)
all$OfficerRace <- gsub("Unknown|m/m", "U", all$OfficerRace)
all$OfficerRace <- gsub("WHITE|WLITE", "W", all$OfficerRace)
all$OfficerRace <- gsub("BLACK", "B", all$OfficerRace)
all$OfficerRace <- gsub("ASIAN", "A", all$OfficerRace)
all$OfficerRace <- gsub("Other|AI/AN|NA/W|Multi-Racial", "O", all$OfficerRace)
all$OfficerRace <- gsub("A/PI ", "A;", all$OfficerRace)
all$OfficerRace <- gsub("A/PI", "A", all$OfficerRace)
all$OfficerRace <- gsub(",", ";", all$OfficerRace)
all$OfficerRace <- gsub(" ", "", all$OfficerRace)
all$OfficerRace <- gsub("A/W|W/L|W/A", "O", all$OfficerRace)
all$OfficerRace[all$OfficerRace == ""] <- "U"

>>>>

# Recode officer races
all$OfficerRace <- gsub("H/L", "L", all$OfficerRace)
all$OfficerRace <- gsub("H", "L", all$OfficerRace)
all$OfficerRace <- gsub("Unknown|m/m", "U", all$OfficerRace)
all$OfficerRace <- gsub("WHITE|WLITE", "W", all$OfficerRace)
all$OfficerRace <- gsub("BLACK", "B", all$OfficerRace)
all$OfficerRace <- gsub("ASIAN", "A", all$OfficerRace)
all$OfficerRace <- gsub("Other|AI/AN|NA/W|Multi-Racial", "O", all$OfficerRace)
all$OfficerRace <- gsub("NA", "O", all$OfficerRace)
all$OfficerRace <- gsub("A/PI ", "A;", all$OfficerRace)
all$OfficerRace <- gsub("A/PI", "A", all$OfficerRace)
all$OfficerRace <- gsub(",", ";", all$OfficerRace)
all$OfficerRace <- gsub(" ", "", all$OfficerRace)
all$OfficerRace <- gsub("A/W|W/L|W/A", "O", all$OfficerRace)
all$OfficerRace[all$OfficerRace == ""] <- "U"

### 2020-11-08 police_modeling.Rmd
data cleaned again

single_victims <- final_df %>% 
  filter(NumberOfSubjects <= 1)

>>>>

# Combining Asian and Other so model will converge
final_df$SubjectRace[final_df$SubjectRace == "A"] <- "O"
final_df$OfficerRace[final_df$OfficerRace == "A"] <- "O"

final_df <- final_df %>% 
  mutate(so = as.numeric(str_count(final_df$SubjectRace, "O|A") > 0),
         oo = as.numeric(str_count(final_df$OfficerRace, "O|A") > 0)) %>% 
  select(-c(sa, oa))

single_victims <- final_df %>% 
  filter(NumberOfSubjects <= 1) %>% 
  mutate(SubjectRace = relevel(as.factor(SubjectRace), "W"))

### 2020-11-08 submissioniii.Rmd
data cleaned again

---
title: "Police Shootings and Racism in America"
author: "Connie Wu"
date: "10/17/2020"
output:
  pdf_document:
    latex_engine: xelatex
---

@@

|        As a basis for this study, I will be using the same dataset that VICE News used. This dataset contains data on officer-involved shootings from 47 of the largest local police departments in America, and more specifically, “information on 4,117 incidents and 4,400 subjects [(victims)] over seven years.” [1] VICE News provides 34 variables in the dataset, including dates ranging from January 2010 to September 2016, 47 unique cities, subject race, subject gender, office race, officer gender, the type of weapon the subject was carrying, and whether the shooting was fatal or not. Race was broken up into 5 categories: White (non-Hispanic) (represented as W), Black (non-Hispanic) (B), Asian (A), Latino (L), Other (O), and Unknown (U). Gender was broken up into 3 categories: Male (M), Female (F), and Unknown (U). Weapon type was broken up into 6 values: "gun", "knife", "replica", "other", "unknown", and "other". Additionally, there were cases in which multiple victims and/or multiple officers were present in the shooting. Each of these scenarios was still represented within one row of the dataset, but semi-colons were present in the respective victim and officer columns, separating each individual's information from each other.

@@

|        After merging the three datasets, the final dataset consists of 2,031 observations.

@@

@@

|        The final model for multiple-victim shootings is written out below:
\begin{center}
$$
log(\frac{p_i}{(1-p_i)}) = \beta_0 + \beta_1\ black\_victim\_present_i + \beta_2\ white\_victim\_present_i +  \beta_3\ latino\_victmi\_present_i +
$$
$$
\beta_4\ (\frac{black_i}{city\_pop_i}) + \beta_{5}\ black\_officer\_present_i + \beta_{6}\ white\_officer\_present_i +
$$
$$
 \beta_{7}\ latino\_officer\_present_i + \beta_{8} \ victim\_armed\_gun_i + \beta_{9} \ white\_officer\_present_i*black\_victim\_present_i
$$
\end{center}

@@

>>>>

---
title: "Police Shootings and Racism in America"
author: "Connie Wu"
date: "11/09/2020"
output:
  pdf_document:
    latex_engine: xelatex
---

@@

|        As a basis for this study, I will be using the same dataset that VICE News used. This dataset contains data on officer-involved shootings from 47 of the largest local police departments in America, and more specifically, “information on 4,117 incidents and 4,400 subjects [(victims)] over seven years.” [1] VICE News provides 34 variables in the dataset, including dates ranging from January 2010 to September 2016, 47 unique cities, subject race, subject gender, office race, officer gender, the type of weapon the subject was carrying, and whether the shooting was fatal or not. Race was broken up into 6 categories: White (non-Hispanic) (represented as W), Black (non-Hispanic) (B), Asian (A), Latino (L), Other (O), and Unknown (U). Gender was broken up into 3 categories: Male (M), Female (F), and Unknown (U). Weapon type was broken up into 5 values: "gun", "knife", "replica", "other", and "unknown". Additionally, there were cases in which multiple victims and/or multiple officers were present in the shooting. Each of these scenarios was still represented within one row of the dataset, but semi-colons were present in the respective victim and officer columns, separating each individual's information from each other.

@@

|        After merging the three datasets, the final dataset consists of 2,054 observations.

@@

***Since A and O are so little in the single victims dataset, I will combine them.

@@

|        The final model for multiple-victim shootings is written out below:
\begin{center}
$$
log(\frac{p_i}{(1-p_i)}) = \beta_0 + \beta_1\ black\_victim\_present_i + \beta_2\ white\_victim\_present_i +  \beta_3\ latino\_victim\_present_i +
$$
$$
\beta_4\ (\frac{black_i}{city\_pop_i}) + \beta_{5}\ black\_officer\_present_i + \beta_{6}\ white\_officer\_present_i +
$$
$$
 \beta_{7}\ latino\_officer\_present_i + \beta_{8} \ victim\_armed\_gun_i + \beta_{9} \ white\_officer\_present_i*black\_victim\_present_i
$$
\end{center}

@@

TO DO: 
- fix my models -- backward selection 
- random effects by city, maybe race | city 
- combine other with asian? 
- more interactions
